Commutative character sheaves and geometric types for supercuspidal representations

### 2017-04-27 Geometric types.tex
After talking with David

Now consider the category $\CSab'(G)$ of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms where $n : G\der\times G\to G$ is the restriction of $m$ to $G\der\times G$ and where $p_n : G\der\times G\to G$ is projection to the second component. \todo{How is $\nu_2$ the same as $\nu$ above?}
Morphisms are morphisms in $\Loc(G)$ commuting with $\mu$ and $\nu$. \todo{Is this definition of morphisms sufficiently clear?} 
Consider the functor
\[
\begin{array}{rcl}
\CS(G\ab) &\to& \CSab'(G) \\
(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L_2(\mu\ab))
\end{array}
\]
Since both $L$ and $L_2$ are equivalences, this functor $\CS(G\ab) \to \CSab'(G)$ is an equivalence of categories.

Let $i : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\times G$ by $j(h) = (i(h),1_G)$. \todo{There's some kind of typo here....}
For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism.
This defines a functor
\[
\begin{array}{rcl}
\CSab'(G) &\to& \CSab(G) \\
(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu)).
\end{array}
\]
Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i(h),g)$.
Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p_n^*\cs{L}$ by
\[
\begin{tikzcd}
& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r} & p_n^*\cs{L} &  \\ 
k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\times 1}
\end{tikzcd}
\]
Then $(\cs{L},\mu,\nu)\in \CSab'(G)$.
It now follows that $\CSab'(G) \to \CSab(G)$ is an equivalence.
\end{proof}

>>>>

Now consider the category $\CSab'(G)$ of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms.
Morphisms are morphisms in $\Loc(G)$ commuting with $\mu$ and $\nu$. 
Consider the functor
\[
\begin{array}{rcl}
\CS(G\ab) &\to& \CSab'(G) \\
(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L_2(\mu\ab))
\end{array}
\]
Since both $L$ and $L_2$ are equivalences, this functor $\CS(G\ab) \to \CSab'(G)$ is an equivalence of categories.

Let $i : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\times G$ by $j(h) = (i(h),1_G)$. 
For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism.
This defines a functor
\[
\begin{array}{rcl}
\CSab'(G) &\to& \CSab(G) \\
(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu)).
\end{array}
\]
Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i(h),g)$.
Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p_n^*\cs{L}$ by
\[
\begin{tikzcd}
& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r} & p_n^*\cs{L} &  \\ 
k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\times 1}
\end{tikzcd}
\]
Then $(\cs{L},\mu,\nu)\in \CSab'(G)$.
It now follows that $\CSab'(G) \to \CSab(G)$ is an equivalence.
\end{proof}
